Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-03 main.tex
rewriting reflection

        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$, then 

@@

        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
        Any $x \in K \cup K^{c}$ has a unique representation
        \begin{align*}
            x = t z_{S} + x^{\perp}, \quad t \in [-1,1], \quad x^{\perp} \in K \cap K^{c},
        \end{align*}
        where we have 
        \begin{align*}
            t = t(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
            .
        \end{align*}
        Based on that observation, we define 
        \begin{align*}
            \Phi_{K}(x) 
			:= 
			x^{\perp} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
            = 
			x^{\perp} - \frac 1 2 \left( \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - 1 \right) z_{S'}
            .
        \end{align*}
        We can write 
        \begin{align*}
            \Phi_{K}(x) 
			:= 
			x^{\perp} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
            = 
			x^{\perp} + t(x) z_{S'} - t(x) z_{S'} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
            = 
			x - t(x) z_{S'} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
            = 
			x - t(x) z_{S'} - \frac 1 2 \left( 3 t(x) - 1 \right) z_{S'}
            .
        \end{align*}
        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
        that satisfies the desired mapping properties. 
        It remains to analyze its Jacobian to get explicit estimates.

        We have an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$.
        With that,
        \begin{align*}
            \Jacobian \Phi_{K}(x)
            &=
            \Id 
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle }  
            z_{S'} \otimes h_{z}^{t}
            \\
            &=
            \Id 
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
            h_{z} \otimes h_{z}^{t}
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
            b_{z} \otimes h_{z}^{t}
            \\
            &=
            \Id 
            - 
            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
            h_{z} \otimes h_{z}^{t}
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
            b_{z} \otimes h_{z}^{t}
            \\
            &=
            \Id 
            - 
            \frac{1}{ 2 } 
            \hat h_{z} \otimes \hat h_{z}^{t}
            - 
            \frac{ \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
            \hat b_{z} \otimes \hat h_{z}^{t}
            .
        \end{align*}
        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
        Hence $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
        \begin{align*}
            C 
            = 
            \frac 1 2 
            \begin{pmatrix}
                -1 & 0 
                \\
                -\tan(\beta) & 2 
            \end{pmatrix}
        \end{align*}
        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
        \begin{align*}
            \sigma_{\max} 
            = 
            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
            =
            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
            ,
            \\
            \sigma_{\min} 
            = 
            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
            =
            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
            .
        \end{align*}
        These are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. 
%         Upon close inspection, we see that 
%         \begin{align*}
%             \sigma_{\max} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
%             ,
%             \\
%             \sigma_{\min} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
%             .
%         \end{align*}
        These are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
        Moreover, $\sigma_{\max} \sigma_{\min} = 1/2$. 
        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
        Similar as above, we use the upper bound 
        \begin{align*}
            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (k+1) \aspectratio(T).
        \end{align*}
        We conclude that 
        \begin{gather*}
            \matnorm{ \Jacobian\Phi_{K} } 
            \leq 
            \frac 1 4 \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 }
            ,
            \\
            \matnorm{ \Jacobian\Phi_{K}^{-1} } 
            \leq 
            \frac 1 2 \sqrt{ 9 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 }
            ,
            \\
            \det \Jacobian\Phi = \frac 1 2 
            .
        \end{gather*}
        This finishes the discussion of the transformation $\Phi$.

        \item 
        We prove another auxiliary result.
        Let $x, h_1, h_2 \in \bbR^{n}$ be non-zero. 
        Define 
        \begin{align*}
            F(x) 
            = 
            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
            \frac{ \langle h_1, x \rangle }{ \| h_1 \|^{2} }
            x
            .
        \end{align*}
        This is defined away from the hyperplane orthogonal to $h_2$.
        This is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
        onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed, 
        if $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.

        We identify the Lipschitz properties of this mapping by computing its Jacobian. 
        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $h_2$, respectively, and the vector $x$.
        In what follows, $y \in \bbR^{n}$.
        \begin{align*}
            \Jacobian F(x) \cdot y
            &=
            \frac{ \langle h_2, h_2 \rangle }{ \|h_2\| \|x\| \cos(\alpha_2) }
            \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
            +
            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
            x
            \\&=
            \frac{ \langle \hat h_2, h_2 \rangle }{ \cos(\alpha_2) }
            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \langle \hat h_2, \hat x \rangle } \hat x \right)
            \frac{ \langle \hat x, \hat h_1 \rangle }{ \langle h_1, \hat h_1 \rangle }
            +
            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
            \hat x
            \\&=
            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
            \frac{ \cos(\alpha_1) }{ \| h_1 \| }
            +
            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
            \hat x
            \\&=
            \frac{ \| h_2 \| }{ \| h_1 \| }
            \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
            \left( 
                y 
                - 
                \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x 
                + 
                \frac{ \langle \hat h_1, y \rangle }{ \cos(\alpha_1) } \hat x 
            \right)
            .
        \end{align*}
        We define $a := \cos(\alpha_1)^{-1} \hat h_1 - \cos(\alpha_2)^{-1} \hat h_2$. 
        Notice that $a \perp \hat x$ by definition. The matrix $\Id + \hat x \otimes a^{t}$ is the identity over the orthogonal complement of the linear span of $a$ and $x$. Over that two-dimensional subspace, it can be represented by a triangular matrix.
        Similar as above, its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are
        %~\cite{blinn1996consider} 
        \begin{align*}
            \sigma_{\max} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2},
            \qquad 
            \sigma_{\min} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}.     
        \end{align*}
        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
        We notice the obvious upper bound 
        \begin{align*}
            \|a\| 
            \leq 
            2 \max_{1 \leq i \leq 2} 
            \left( 
                \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
            \right)
            .
        \end{align*}

        \item 
        We introduce a bi-Lipschitz mapping 
        \begin{align*}
            \Psi : |\calR'| \rightarrow |\calK|
        \end{align*}
        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$. We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively. They define respective hyperplanes $H_{G}$ and $H_{K}$,
        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$. 
        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$. 
        We define 
        \begin{align*}
            \Psi(x) 
            = 
            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
            x
            .
        \end{align*}
        One easily verifies that this defines a continuous mapping $\Psi$. 
        By the same line of thought, we see that it is invertible with inverse satisfying 
        \begin{align*}
            \Psi^{-1}(z) 
            = 
            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
            z,
            \qquad 
            z = \Psi(x)
            .
        \end{align*}
        Our previous observations enable estimates for the Jacobians. 
        We have the operator norm and determinant formulas 
        \begin{gather*}
            \matnorm{ \Jacobian\Psi(x) }
            = 
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \left( 
                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
            \right)
            \\
            \matnorm{ \Jacobian\Psi(z)^{-1} }
            = 
            \frac{ \| h_{{G}} \| }{ \| h_K \| }
            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
            \left( 
                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
            \right)^{-1},
            \\
            \det\Jacobian\Psi(x)
            =
            \left( 
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \right)^{n},
            \qquad
            \det\Jacobian\Psi^{-1}(x)
            =
            \left( 
            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
            \right)^{n}
        \end{gather*}
        where $\alpha_K$ and $\alpha_{{G}}$ are the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
        and where 
        \begin{align*}
            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
            .
        \end{align*}
        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
        By the definition of the cosine, 
        \begin{align*}
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \leq 
            \frac{ \| x_K \| }{ \| h_{{G}} \| }
            \leq 
            \frac{ \diam(K) }{ \| h_{{G}} \| }
            ,
            \qquad 
            \frac{ \| h_{{G}} \| }{ \| h_K \| }
            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
            \leq 
            \frac{ \| x_{G} \| }{ \| h_{K} \| }
            \leq 
            \frac{ \diam(G) }{ \| h_{K} \| }
            .
        \end{align*}
%         \begin{align*}
%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
%             \leq 
%             \frac{ \| x_K \| }{ \| x_{{G}} \| }
%             .
%         \end{align*}

>>>>

        If we orthogonally decompose $z_{S'} = h_{z} + b_{z}$ for some $b_{z} \in \bbR^{n}$, then 

@@

        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
        Here, we let $Q \subseteq K \cap K^{c}$ be the subsimplex 
        that is complementary to the line segment from the origin to $z_{S'}$ in $K$.
        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $K^{c}$.
        From the very definition of simplices, we now conclude that any $x \in K \cup K^{c}$ 
        has a unique representation
        \begin{align*}
            x = \lambda z_{S} + \mu x^{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x^{Q} \in Q,
        \end{align*}
        Since $\mu x^{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
        \begin{align*}
            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
            .
        \end{align*}
        Based on that observation, we define 
        \begin{align*}
            \Phi_{K}(x) 
			&
			:= 
            \mu x^{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
            \\&
            = 
            x - \left( \frac 3 2 \lambda(x) - \frac 1 2 \right) z_{S'}
            = 
            x - \left( \frac 3 2 \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - \frac 1 2 \right) z_{S'}
            .
        \end{align*}
        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
        that satisfies the desired mapping properties. 
        It remains to analyze its Jacobian to get explicit estimates.

        We once more introduce an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$ for some $b_{z} \in \bbR^{n}$.
        With that,
            \Jacobian \Phi_{K}(x)
            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle }  
            z_{S'} \otimes h_{z}^{t}
            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle } 
            h_{z} \otimes h_{z}^{t}
            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle } 
            b_{z} \otimes h_{z}^{t}
            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
            h_{z} \otimes h_{z}^{t}
            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 
            b_{z} \otimes h_{z}^{t}
            \frac{3}{ 2 } 
            \hat h_{z} \otimes \hat h_{z}^{t}
            \frac{ 3 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 
            \hat b_{z} \otimes \hat h_{z}^{t}
        The Jacobian acts as the identity over the span of $h_{z}$ and $z_{s'}$.
		We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
        Hence $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 
            C 
                -\frac 1 2             & 0 
                -\frac 3 2 \tan(\beta) & 2 
			\frac 1 2 
                -3\tan(\beta) & 2 
        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
            \sigma_{\max} 
            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
            \sigma_{\min} 
            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
            \sigma_{\max} 
            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
            %=
            %\frac 1 4 \sqrt{ 9 + 9\tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
            \sigma_{\min} 
            \sqrt{ \frac{ 9\tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ 81\tan(\beta)^{4} + 90 \tan(\beta)^{2} + 9 } }
            \frac 3 4 \sqrt{ 1 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + 9\tan(\beta)^2 }
        Notice that $\sigma_{\max} \sigma_{\min} = 1/2$. 
        These are monotonely increasing from $1$ and decreasing from $0.5$, respectively, in $\tan(\beta)$. 
        Hence, these are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. Therefore,
            \det \Jacobian\Phi = \frac 1 2.
        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
        Similar as above, we use the upper bound 
            \tan(\beta) = \frac{\vecnorm{ b_{z} }}{\vecnorm{ h_{z} }} \leq (k+1) \aspectratio(T).
        We conclude that 
            \matnorm{ \Jacobian\Phi_{K} } 
            \frac 3 4 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
            \matnorm{ \Jacobian\Phi_{K}^{-1} } 
            \frac 3 2 \sqrt{ 1 + (k+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(k+1)^2 \aspectratio(T)^2 }
        This finishes the discussion of the transformation $\Phi$.

        \item 
        We continue with an auxiliary result.
        Let $x, h_1, h_2 \in \bbR^{n}$ be non-zero. 
        Define 
        \begin{align*}
            F(x) 
            = 
            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
            \frac{ \langle h_1, x \rangle }{ \| h_1 \|^{2} }
            x
            .
        \end{align*}
        This is defined away from the hyperplane orthogonal to $h_2$.
        If $x \in \bbR^{n}$ with $\langle h_1, x \rangle = \| h_1 \|^{2}$, then $\langle F(x), h_2 \rangle = \| h_2 \|^{2}$.
        That shows that $F(x)$ is a radial mapping that maps each point on the hyperplane defined by the normal vector $h_1$
        onto the colinear point that lies on the hyperplane defined by the normal vector $h_2$. Indeed,

        We identify the Lipschitz properties of this mapping by computing its Jacobian. 
        We write $\alpha_1, \alpha_2 \geq 0$ for the two angles between $h_1$ and $x$ and between $h_2$ and $x$, respectively. 
        In what follows, $y \in \bbR^{n}$.
        \begin{align*}
            \Jacobian F(x) \cdot y
            &=
            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
            x
            - 
            \frac{ \langle h_2, h_2 \rangle \langle h_2, y \rangle }{ \langle h_2, x \rangle^{2} }
            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
            x 
            +
            \frac{ \langle h_2, h_2 \rangle }{ \langle h_2, x \rangle }
            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
            y 
            \\&=
            \frac{ \langle h_2, h_2 \rangle }{ \|h_2\| \|x\| \cos(\alpha_2) }
            \left( y - \frac{ \langle h_2, y \rangle }{ \langle h_2, x \rangle } x \right)
            \frac{ \langle x, h_1 \rangle }{ \langle h_1, h_1 \rangle }
            +
            \frac{ \| h_2 \|^{2} }{ \langle h_2, x \rangle }
            \frac{ \langle h_1, y \rangle }{ \| h_1 \|^{2} }
            x
            \\&=
            \frac{ \langle \hat h_2, h_2 \rangle }{ \cos(\alpha_2) }
            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \langle \hat h_2, \hat x \rangle } \hat x \right)
            \frac{ \langle \hat x, \hat h_1 \rangle }{ \langle h_1, \hat h_1 \rangle }
            +
            \frac{ \| h_2 \| }{ \langle \hat h_2, \hat x \rangle }
            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
            \hat x
            \\&=
            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
            \left( y - \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x \right)
            \frac{ \cos(\alpha_1) }{ \| h_1 \| }
            +
            \frac{ \| h_2 \| }{ \cos(\alpha_2) }
            \frac{ \langle \hat h_1, y \rangle }{ \| h_1 \| }
            \hat x
            \\&=
            \frac{ \| h_2 \| }{ \| h_1 \| }
            \frac{ \cos(\alpha_1) }{ \cos(\alpha_2) }
            \left( 
                y 
                - 
                \frac{ \langle \hat h_2, y \rangle }{ \cos(\alpha_2) } \hat x 
                + 
                \frac{ \langle \hat h_1, y \rangle }{ \cos(\alpha_1) } \hat x 
            \right)
            .
        \end{align*}
        We define $a := \cos(\alpha_1)^{-1} \hat h_1 - \cos(\alpha_2)^{-1} \hat h_2$. 
        Notice that $a \perp \hat x$. The matrix $\Id + \hat x \otimes a^{t}$ is the identity over the orthogonal complement of the linear span of $a$ and $x$. Over that two-dimensional subspace, it can be represented by a triangular matrix.
        Similar as above, its largest and the smallest singular values $\sigma_{max} \geq 1 \geq \sigma_{\min}$ are
        %~\cite{blinn1996consider} 
        \begin{align*}
            \sigma_{\max} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2},
            \qquad 
            \sigma_{\min} = \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}.     
        \end{align*}
        Notice that these are strictly monotonely increasing or decreasing, respectively, in $\|a\|$.
        We thus consider the upper bound 
        \begin{align*}
            \|a\| 
            \leq 
            2 \max_{1 \leq i \leq 2} 
            \left( 
                \frac{ \hat h_i }{ \langle \hat x, \hat h_i \rangle } 
            \right)
            .
        \end{align*}

        \item 
		\mwl{Continue proof reading here.}
        We introduce a bi-Lipschitz mapping 
        \begin{align*}
            \Psi : |\calR'| \rightarrow |\calK|
        \end{align*}
        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$. We let $h_{{G}}$ and $h_{K}$ be the normals of the origin within ${G}$ and $K$, respectively. They define respective hyperplanes $H_{G}$ and $H_{K}$,
        and we write $F_{G} = G \cap H_{G}$ and $F_{K} = K \cap H_{K}$. 
        We notice that $x$ has a sharp angle to both $h_{{G}}$ and $h_{K}$. 
        We define 
        \begin{align*}
            \Psi(x) 
            = 
            \frac{ \| h_K \|^{2} }{ \langle h_K, x \rangle }
            \frac{ \langle h_{{G}}, x \rangle }{ \| h_{{G}} \|^{2} }
            x
            .
        \end{align*}
        One easily verifies that this defines a continuous mapping $\Psi$. 
        By the same line of thought, we see that it is invertible with inverse satisfying 
        \begin{align*}
            \Psi^{-1}(z) 
            = 
            \frac{ \| h_{{G}} \|^{2} }{ \langle h_{{G}}, z \rangle }
            \frac{ \langle h_K, z \rangle }{ \| h_K \|^{2} }
            z,
            \qquad 
            z = \Psi(x)
            .
        \end{align*}
        Our previous observations enable estimates for the Jacobians. 
        We have the operator norm and determinant formulas 
        \begin{gather*}
            \matnorm{ \Jacobian\Psi(x) }
            = 
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \left( 
                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } + \frac{ \|a\| }{2}
            \right)
            \\
            \matnorm{ \Jacobian\Psi(z)^{-1} }
            = 
            \frac{ \| h_{{G}} \| }{ \| h_K \| }
            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
            \left( 
                \sqrt{ 1 + \frac{ \|a\|^{2} }{ 4 } } - \frac{ \|a\| }{2}
            \right)^{-1},
            \\
            \det\Jacobian\Psi(x)
            =
            \left( 
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \right)^{n},
            \qquad
            \det\Jacobian\Psi^{-1}(x)
            =
            \left( 
            \frac{ \| h_{{G}} \| }{ \| h_{K} \| }
            \frac{ \cos(\alpha_{K}) }{ \cos(\alpha_{{G}}) }
            \right)^{n}
        \end{gather*}
        where $\alpha_K$ and $\alpha_{{G}}$ are the angles of $x$ with the vectors $h_{{G}}$ and $h_{K}$, respectively,
        and where 
        \begin{align*}
            a := \cos(\alpha_{{G}})^{-1} \hat h_{{G}} - \cos(\alpha_K)^{-1} \hat h_K
            .
        \end{align*}
        We let $x_{G} \in F_{G}$ and $x_{K} \in F_{K}$ be the intersection points of the ray $\bbR \cdot x$ with the respective faces.
        By the definition of the cosine, 
        \begin{align*}
            \frac{ \| h_K \| }{ \| h_{{G}} \| }
            \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
            \leq 
            \frac{ \| x_K \| }{ \| h_{{G}} \| }
            \leq 
            \frac{ \diam(K) }{ \| h_{{G}} \| }
            ,
            \qquad 
            \frac{ \| h_{{G}} \| }{ \| h_K \| }
            \frac{ \cos(\alpha_K) }{ \cos(\alpha_{{G}}) }
            \leq 
            \frac{ \| x_{G} \| }{ \| h_{K} \| }
            \leq 
            \frac{ \diam(G) }{ \| h_{K} \| }
            .
        \end{align*}
%         \begin{align*}
%             \frac{ \| h_K \| }{ \| h_{{G}} \| }
%             \frac{ \cos(\alpha_{{G}}) }{ \cos(\alpha_K) }
%             \leq 
%             \frac{ \| x_K \| }{ \| x_{{G}} \| }
%             .
%         \end{align*}
